EvoSwarm: An Event-based Architecture for Multi-population Optimization Algorithms

### 2020-05-05 draft.tex

\subsection{EvoSwarm from the developer point of view}

Developers can add new algorithm as stateless functions in
several ways and with two levels of integration. In the first level of
integration, the algorithm execution is not dependent on an initial
configuration created in the setup, and it only needs to take messages from the
input queue and return the modified population to the output queue. On the
second level, the algorithm receives a configuration from the initial setup,
specifying initial algorithm parameters. We show an example of the configuration
file received by workers in Figure x. % Adding to Annex or is not even needed? - M

% Clarify this is the first level.
In the case of a decoupled worker, developers can implement a new stateless
Docker container that executes a daemon that continuously pulls messages from the
input queue on the Redis host specified as an environmental variable {\tt REDIS\_HOST}.
If the function is written in Python, developers can base the implementation on
the provided worker container image, adding a new type of function.  
If developers use an existing library for population-based algorithms, they need
to change the standard model of execution, that first creates a random
population because, in this case, we need to start with the population provided
as a parameter. Depending on the implementation, it required to extract the
population from the JSON message and create the population object needed by the
library. Again, the state of the population must be encoded as a JSON message to
be returned as a result. Depending on the type of experiment, additional data
can be returned in the message. For instance, the message can include the id of
the container, or even records giving information for each iteration of the
algorithm. The format of the JSON message is depicted in Figure y. % Adding to Annex or is not even needed? - M
% it's probably OK if you add it, but instead of Figure it could be a listing - JJ

>>>>

\subsection{Developer}

Developers can add new algorithm stateless functions in
several ways and with two levels of integration. In the first level of
integration, the algorithm execution is not dependent on an initial
configuration created in the setup, and it only needs to take messages from the
input queue and return the modified population to the output queue. On the
second level, the algorithm receives a configuration from the initial setup,
specifying initial algorithm parameters. We show an example of the configuration
file received by workers in Figure x. % Adding to Annex or is not even needed? - M
In the case of a decoupled worker, developers can implement a new stateless
docker container that executes a demon that continuously pulls messages from the
input queue on the Redis host specified as an environmental variable {\tt REDIS\_HOST}.
If the function is written in python, developers can base the implementation on
the provided worker container image, adding a new type of function.  
If developers use an existing library for population-based algorithms, they need
to change the standard model of execution, that first creates a random
population because, in this case, we need to start with the population provided
as a parameter. Depending on the implementation, it required to extract the
population from the JSON message and create the population object needed by the
library. Again, the state of the population must be encoded as a JSON message to
be returned as a result. Depending on the type of experiment, additional data
can be returned in the message. For instance, the message can include the id of
the container, or even records giving information for each iteration of the
algorithm. The format of the JSON message is depicted in Figure y. % Adding to Annex or is not even needed? - M
